Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
pre pull

\begin{figure}[!htbp]
  \begin{center}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l3_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l2_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l1_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l0_a}}
  \end{center}
  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
  %
  For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
  \label{fig:refine}
\end{figure}
\todo[inline]{blabla experiments}

@@

@@

\todo[inline]{blabla experiments}

For dynamic datasets, we consider a time varying impicit
surface. Since it would have been to expensive to update the a mipmap texture
of densities at each time step, we simply evaluate the implicit
expression at each vertex of a cell to decide if such cell is included
or not into $\Ball{R}{\vx}\cap \Shape$.
\todo[inline]{blabla experiments}

>>>>

\begin{figure}[!htbp]
  \begin{center}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l3_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l2_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l1_a}}
   {\includegraphics[width=2.7cm]{figs/octa_r10_l0_a}}
  \end{center}
  \caption{Illustration of mean curvature computation on an OctaFlower (digital domain of $130^3$) using mipmap approximation with different levels : $l_3$, $l_2$, $l_1$ and $l_0$ (\ie no approximation).
  %
  For all illustrations, we use directly normal vectors computed by algorithm discussed in Section~\ref{sec:curv-tens-estim}}
  \label{fig:refine}
\end{figure}

@@

In this experiments, we measure the timings obtained when running our framework on a
GeForce GTX 850M. Here, the triangulation is dynamically refining according to its distance to the camera.
At each frame, both the curvature and the triangulation are recomputed.
If the visualisation stays unchanged, we compute the curvature at a level $l-1$ until the level $l_0$ is reached.
We measured those timings using the regular and the hierarchical algorithm. The results are presented
figure \ref{fig:timings}.

\subsection{Visualisation}

For dynamic datasets, we consider a time varying implicit
surface. Since it would have been to expensive to update the a mipmap texture
of densities at each time step, we simply evaluate the implicit
expression at each vertex of a cell to decide if such cell is included
or not into $\Ball{R}{\vx}\cap \Shape$.
\todo[inline]{blabla experiments}

@@
